Studies of quantum dots

### 2017-01-17 Manuscript/paper.tex
Consolidate data even more
Add fig-methods

\begin{figure}
  % [width=.48\textwidth]
  \includegraphics[width=\textwidth]{figures/fig-shell-structure-v2}
  \caption{Visualization of the 20 lowest single-particle states in the 2D harmonic oscillator basis.  Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.  The $n$ quantum number increases upward vertically, starting at zero for the lowest state within a each column.}
  \label{fig:shell-structure}
\end{figure}

@@

By expanding the commutator in \eqref{eq:imsrgode} without consideration of the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
\begin{align}
    \frac{\D H^{[r]}}{\D s} = C^{[r]}(\eta, H) \label{eq:flowmxe}
\end{align}
where
\begin{align}
  C^{[r]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$}
\end{align}
and finally
\begin{align}
  D^{[0]}(A, B)
  &\equiv
    \sum_{i, a} n_i \bar{n}_a A^{[1]}_{i, a} B^{[1]}_{a, i}
    + \frac{1}{4} \sum_{i, j, a, b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i, j, a, b} B^{[2]}_{a, b, i, j}
    \label{eq:flow0} \\
  D^{[1]}_{p, q}(A, B)
  &\equiv
    \sum_{r} A^{[1]}_{p, r} B^{[1]}_{r, q}
    - \frac{1}{2} \sum_{i, j, a} n_i n_j \bar{n}_a A^{[2]}_{i, j, a, q} B^{[2]}_{a, p, i, j}
    + \frac{1}{2} \sum_{i, a, b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i, p, a, b} B^{[2]}_{a, b, i, q}
    \notag \\
  &\hphantom{=}
    + \sum_{i, a} n_i \bar{n}_a \left(
    A^{[1]}_{i, a} B^{[2]}_{a, p, i, q}
    + A^{[2]}_{i, p, a, q} B^{[1]}_{a, i}
    \right)
    \label{eq:flow1} \\
  D^{[2]}_{p, q, r, s}(A, B)
  &\equiv
    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s}
    \sum_{i, a} n_i \bar{n}_a A^{[2]}_{i, p, a, r} B^{[2]}_{a, q, i, s}
    + \frac{1}{2} \sum_{i, j} n_i n_j A^{[2]}_{i, j, r, s} B^{[2]}_{p, q, i, j}
    + \frac{1}{2} \sum_{a, b} \bar{n}_a \bar{n}_b A^{[2]}_{p, q, a, b} B^{[2]}_{a, b, r, s}
    \notag \\
  &\hphantom{=}
    + \sum_{t} \left(
    \tilde{\mathcal{A}}_{p, q} A^{[1]}_{q, t} B^{[2]}_{p, t, r, s}
    + \tilde{\mathcal{A}}_{r, s} A^{[2]}_{p, q, r, t} B^{[1]}_{t, s}
    \right)
    \label{eq:flow2}
\end{align}
\begin{figure}
\includegraphics[width=.48\textwidth]{fig-diagrams-imsrg}
\caption{Diagrammatic representation of $C^{[r]}(\circ, \bullet)$ in \eqref{eq:commutmxe} that forms part of the IM-SRG flow equation \eqref{eq:flowmxe}.  The diagrams are implicitly antisymmetrized (Hugenholtz diagrams \cite{HUGENHOLTZ1957481} as described in \cite{shavitt2009many} \S 4.4.3).}
\label{fig:diagrams-imsrg}
\end{figure}
The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem [[ref]] or, even more efficiently, diagrammatic techniques [[ref]] to arrive at the results.  In particular, the diagrammatic representation of antisymmetrized matrix elements are shown in Figure \ref{fig:diagrams-imsrg}.

@@

\begin{figure}
\includegraphics[width=.48\textwidth]{fig-diagrams-sfe}
\caption{Diagrammatic form of the second- and third-order QDPT corrections.  The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.}
\label{fig:diagrams-sfe}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[Results for $N=6$ and $\omega=1.0$]{
    \label{fig:N6hw1}
    \includegraphics[width=0.38\textwidth]{figures/6parthw1.pdf}
  }
  \subfigure[Results for $N=6$ and $\omega=0.5$]{
    \label{fig:N6hw05}
    \includegraphics[width=0.38\textwidth]{figures/6parthw05.pdf}
  } \\
  \subfigure[Results for $N=6$ and $\omega=0.28$]{
    \label{fig:N6hw028}
    \includegraphics[width=0.38\textwidth]{figures/6parthw028.pdf}
  }
  \subfigure[Results for $N=6$ and $\omega=0.1$]{
    \label{fig:N6hw01}
    \includegraphics[width=0.38\textwidth]{figures/6parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=6$ and $\omega=1.0$ The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$. A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator. All energies in atomic units.}
  \label{fig:N6}
\end{figure}

\begin{figure}
  \centering
  \subfigure[Results for $N=12$ and $\omega=1.0$]{
    \label{fig:N12hw1}
    \includegraphics[width=0.38\textwidth]{figures/12parthw1.pdf}
  }
  \subfigure[Results for $N=12$ and $\omega=0.5$]{
    \label{fig:N12hw05}
    \includegraphics[width=0.38\textwidth]{figures/12parthw05.pdf}
  } \\
  \subfigure[Results for $N=12$ and $\omega=0.28$]{
    \label{fig:N12hw028}
    \includegraphics[width=0.38\textwidth]{figures/12parthw028.pdf}
  }
  \subfigure[Results for $N=12$ and $\omega=0.1$]{
    \label{fig:N12hw01}
    \includegraphics[width=0.38\textwidth]{figures/12parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=12$ and different values of $\omega$. The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$. A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator. All energies in atomic units.}
  \label{fig:N12}
\end{figure}

\begin{figure}
  \centering
  \subfigure[Results for $N=20$ and $\omega=1.0$]{
    \label{fig:N20hw1}
    \includegraphics[width=0.38\textwidth]{figures/20parthw1.pdf}
  } \subfigure[Results for $N=20$ and $\omega=0.5$]{
    \label{fig:N20hw05}
    \includegraphics[width=0.38\textwidth]{figures/20parthw05.pdf}
  } \\
  \subfigure[Results for $N=20$ and $\omega=0.28$]{
    \label{fig:N20hw028}
    \includegraphics[width=0.38\textwidth]{figures/20parthw028.pdf}
  } \subfigure[Results for $N=20$ and $\omega=0.1$]{
    \label{fig:N20hw01}
    \includegraphics[width=0.38\textwidth]{figures/20parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
    for circular quantum dots for $N=20$ and different values of
    $\omega$. The results are compared with diffusion Monte
    Carlo (DMC), coupled cluster at the level of singles and doubles
    (CCSD), full configuration interaction (FCI) and Hartree-Fock
    calculations (HF) as functions of the number of major oscillator
    shells $R$. A harmonic oscilaltor basis has been used, with an
    unrenormalized Coulomb repulsion and the White generator. All
    energies in atomic units.}
  \label{fig:N20}
\end{figure}

\begin{figure}
  \centering
  \subfigure[Results for $N=30$ and $\omega=1.0$]{
    \label{fig:N30hw1}
    \includegraphics[width=0.38\textwidth]{figures/30parthw1.pdf}
  } \subfigure[Results for $N=30$ and $\omega=0.5$]{
    \label{fig:N30hw05}
    \includegraphics[width=0.38\textwidth]{figures/30parthw05.pdf}
  } \\
  \subfigure[Results for $N=30$ and $\omega=0.28$]{
    \label{fig:N30hw028}
    \includegraphics[width=0.38\textwidth]{figures/30parthw028.pdf}
  } \subfigure[Results for $N=30$ and $\omega=0.1$]{
    \label{fig:N30hw01}
    \includegraphics[width=0.38\textwidth]{figures/30parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG)
    for circular quantum dots for $N=30$ and different values of
    $\omega$. The results are compared with diffusion Monte
    Carlo (DMC), coupled cluster at the level of singles and doubles
    (CCSD), full configuration interaction (FCI) and Hartree-Fock
    calculations (HF) as functions of the number of major oscillator
    shells $R$. A harmonic oscilaltor basis has been used, with an
    unrenormalized Coulomb repulsion and the White generator. All
    energies in atomic units.}
  \label{fig:N30}
\end{figure}

\begin{figure}
  \centering
  \subfigure[Results for $N=42$ and $\omega=1.0$]{
    \label{fig:N42hw1}
    \includegraphics[width=0.38\textwidth]{figures/42parthw1.pdf}
  } \subfigure[Results for $N=42$ and $\omega=0.5$]{
    \label{fig:N42hw05}
    \includegraphics[width=0.38\textwidth]{figures/42parthw05.pdf}
  } \\
  \subfigure[Results for $N=42$ and $\omega=0.28$]{
    \label{fig:N42hw028}
    \includegraphics[width=0.38\textwidth]{figures/42parthw028.pdf}
  } \subfigure[Results for $N=42$ and $\omega=0.1$]{
    \label{fig:N42hw01}
    \includegraphics[width=0.38\textwidth]{figures/42parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=42$ and different values of $\omega$. The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$. A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator. All energies in atomic units.}
  \label{fig:N42}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{fig-gs}
  \caption{Ground state energies.}
  \label{fig:gs}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{fig-add}
  \caption{Addition energies.}
  \label{fig:add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{fig-rm}
  \caption{Removal energies.}
  \label{fig:rm}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{fig-rel-slopes}
  \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.  The key observation from this plot is that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
  \label{fig:rel-slopes}
\end{figure}

@@

@@

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig-shell-structure-v2}
  \caption{Visualization of the 20 lowest single-particle states in the 2D harmonic oscillator basis.  Each box represents a single-particle state arranged by $m_\ell$, $m_{\mathrm{s}}$, and energy, and the up/down arrows indicate the spin of the states.  The $n$ quantum number increases upward vertically, starting at zero for the lowest state within a each column.}
  \label{fig:shell-structure}
\end{figure}

@@

By expanding the commutator in \eqref{eq:imsrgode} without consideration of the three-body term, we obtain the matrix-element form of the IM-SRG(2) flow equation:
\begin{align}
    \frac{\D H^{[r]}}{\D s} = C^{[r]}(\eta, H) \label{eq:flowmxe}
\end{align}
where
\begin{align}
  C^{[r]}(A, B) &\equiv 2 \mathcal{A}_{A, B} D^{[r]}(A, B) \text{ for any $r$, $A$, $B$} \label{eq:commutmxe} \\
  \mathcal{A}_{x, y} f(x, y) &\equiv \frac{1}{2} \bigl(f(x, y) - f(y, x)\bigr) \text{ for any $x$, $y$, $f$}
\end{align}
and finally
\begin{align}
  D^{[0]}(A, B)
  &\equiv
    \sum_{i, a} n_i \bar{n}_a A^{[1]}_{i, a} B^{[1]}_{a, i}
    + \frac{1}{4} \sum_{i, j, a, b} n_i n_j \bar{n}_a \bar{n}_b A^{[2]}_{i, j, a, b} B^{[2]}_{a, b, i, j}
    \label{eq:flow0} \\
  D^{[1]}_{p, q}(A, B)
  &\equiv
    \sum_{r} A^{[1]}_{p, r} B^{[1]}_{r, q}
    - \frac{1}{2} \sum_{i, j, a} n_i n_j \bar{n}_a A^{[2]}_{i, j, a, q} B^{[2]}_{a, p, i, j}
    + \frac{1}{2} \sum_{i, a, b} n_i \bar{n}_a \bar{n}_b A^{[2]}_{i, p, a, b} B^{[2]}_{a, b, i, q}
    \notag \\
  &\hphantom{=}
    + \sum_{i, a} n_i \bar{n}_a \left(
    A^{[1]}_{i, a} B^{[2]}_{a, p, i, q}
    + A^{[2]}_{i, p, a, q} B^{[1]}_{a, i}
    \right)
    \label{eq:flow1} \\
  D^{[2]}_{p, q, r, s}(A, B)
  &\equiv
    \tilde{\mathcal{A}}_{p, q} \tilde{\mathcal{A}}_{r, s}
    \sum_{i, a} n_i \bar{n}_a A^{[2]}_{i, p, a, r} B^{[2]}_{a, q, i, s}
    + \frac{1}{2} \sum_{i, j} n_i n_j A^{[2]}_{i, j, r, s} B^{[2]}_{p, q, i, j}
    + \frac{1}{2} \sum_{a, b} \bar{n}_a \bar{n}_b A^{[2]}_{p, q, a, b} B^{[2]}_{a, b, r, s}
    \notag \\
  &\hphantom{=}
    + \sum_{t} \left(
    \tilde{\mathcal{A}}_{p, q} A^{[1]}_{q, t} B^{[2]}_{p, t, r, s}
    + \tilde{\mathcal{A}}_{r, s} A^{[2]}_{p, q, r, t} B^{[1]}_{t, s}
    \right)
    \label{eq:flow2}
\end{align}
\begin{figure}
\includegraphics[width=.48\linewidth]{fig-diagrams-imsrg}
\caption{Diagrammatic representation of $C^{[r]}(\circ, \bullet)$ in \eqref{eq:commutmxe} that forms part of the IM-SRG flow equation \eqref{eq:flowmxe}.  The diagrams are implicitly antisymmetrized (Hugenholtz diagrams \cite{HUGENHOLTZ1957481} as described in \cite{shavitt2009many} \S 4.4.3).}
\label{fig:diagrams-imsrg}
\end{figure}
The equations can be derived directly from the anticommutation relations of the field operators, but it is more convenient to use Wick's theorem [[ref]] or, even more efficiently, diagrammatic techniques [[ref]] to arrive at the results.  In particular, the diagrammatic representation of antisymmetrized matrix elements are shown in Figure \ref{fig:diagrams-imsrg}.

@@

\begin{figure}
\includegraphics[width=.48\linewidth]{fig-diagrams-sfe}
\caption{Diagrammatic form of the second- and third-order QDPT corrections.  The diagrams are implicitly antisymmetrized (Hugenholtz diagrams), but also have implicit denominators as with many-body perturbation theory.}
\label{fig:diagrams-sfe}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[Results for $N=6$ and $\omega=1.0$]{
    \label{fig:N6hw1}
    \includegraphics[width=0.38\linewidth]{figures/6parthw1.pdf}
  }
  \subfigure[Results for $N=6$ and $\omega=0.5$]{
    \label{fig:N6hw05}
    \includegraphics[width=0.38\linewidth]{figures/6parthw05.pdf}
  } \\
  \subfigure[Results for $N=6$ and $\omega=0.28$]{
    \label{fig:N6hw028}
    \includegraphics[width=0.38\linewidth]{figures/6parthw028.pdf}
  }
  \subfigure[Results for $N=6$ and $\omega=0.1$]{
    \label{fig:N6hw01}
    \includegraphics[width=0.38\linewidth]{figures/6parthw01.pdf}
  }
  \caption{Comparison of our IM-SRG(2) ground state energies (SRG) for circular quantum dots for $N=6$ and $\omega=1.0$ The results are compared with diffusion Monte Carlo (DMC), coupled cluster at the level of singles and doubles (CCSD), full configuration interaction (FCI) and Hartree-Fock calculations (HF) as functions of the number of major oscillator shells $R$. A harmonic oscilaltor basis has been used, with an unrenormalized Coulomb repulsion and the White generator. All energies in atomic units.}
  \label{fig:N6}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fig-gs}
  \caption{Ground state energies.}
  \label{fig:gs}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fig-add}
  \caption{Addition energies.}
  \label{fig:add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fig-rm}
  \caption{Removal energies.}
  \label{fig:rm}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fig-rel-slopes}
  \caption{Comparison of the rate of convergence for various modifications to the Coulomb interaction.  The key observation from this plot is that the short-range part of the interaction has a strong impact on the convergence, whereas the long-range tail has little effect.}
  \label{fig:rel-slopes}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/fig-methods}
  \caption{A high-level view of the ways in which many-body methods in this paper can be combined to calculate ground state, addition, and removal energies, shown as a directed acyclic graph.}
  \label{fig:methods}
\end{figure}

Figure \ref{fig:methods} shows high-level view of the ways in which many-body methods in this paper can be combined to to compute the energy observables.  There are many possible paths through which one can walk in this directed graph to obtain the output observables.  For example, one can do HF to get an initial rough estimate, followed by IM-SRG to refine the ground state, and then EOM to refine the addition and removal energies.  This is in fact one of the approaches benchmarked in this paper.

It is possible to omit some of the methods, bypassing some of the steps.  For example, one can do an IM-SRG calculation \emph{without} doing HF.  There are few good reasons to do so, as it typically worsens the result and increases the numerical cost of IM-SRG, but it can be done.  Similarly, one can do both HF and IM-SRG, but omit QDPT, yet still obtain \emph{addition and removal} energies.  The result would be poor, but it may be useful for the purpose of assessing difficulty of the problem.  For example, if the omission of QDPT leads to a large change, then it may indicate the presence of strong correlations.

@@

[[Cite as source of DMC energies: \cite{PhysRevB.84.115302}]]
